A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Use g+h in big-O notation, avoiding need to define n

Let $G$ and $H$ be the two input graphs to our maximum common subgraph problem.
The orders (vertex counts) of these graphs are denoted $g$ and $h$. We will
use $n$ in complexity results to denote $\max(g + h)$ ?? WTF James? Help?.

@@

\paragraph{Efficient representation of label classes} The algorithm as
described so far apparently requires $\BigO{n^2}$ space at each level of the
search tree.  We can reduce the memory requirement to $\BigO{n}$ per level by
storing a \emph{label class} as a pair $\langle P,T \rangle$ for each label $l$
that is used, where $P$ is the set of vertices in $\V(G)$ labelled $l$, and $T$
is the set of vertices in $\V(H)$ labelled $l$\footnote{We adopt terminology
from subgraph isomorphism, where one graph is a pattern graph $P$ and the other
the target graph $T$.}. Since there are $g + h$ vertices in the two graphs, at
most $g + h$ label classes can exist at once, and there are at most $g + h$
vertices in the union of all of the $P$ and $T$ sets.  We can gain further
efficiency by discarding during search any label class that has an empty $P$ or
$T$ set.

@@

\paragraph{Undirected with edge labels} Each adjacency matrix
entry contains an edge label, or a null entry (non-adjacent) $0$.
We use \cref{labDirAlg}, by letting $L$ be
the union of $\{0\}$ with the set of all labels that appear in the input
graphs. Since there may be up to $g + h$ distinct labels, the loop in
\cref{labDirAlg} may execute up to $g + h$ times and
requires $\BigO{n^2}$ time per search
node.  It is possible to modify the algorithms to run in $\BigO{n \log n}$ per
search node.  First, run lines 17-19
of \cref{McCliqueAlg} to create a new label-class of vertices that are not
adjacent to $v$ or $w$, and remove these vertices from $\langle P',T' \rangle$.
Next, sort $P'$ and $T'$ in ascending order of the label on the edge from $v$
or $w$ to each vertex. We can then create the label classes corresponding to
each edge label by simultaneously traversing $P'$ and $T'$ from left to right.

@@

\McSplit\ requires $\BigO{n}$ time at each search node, and does not require
any auxiliary data structures larger than the adjacency matrices of $G$ and $H$
to be built prior to search.  CP-FC requires $\BigO(?????)$ \dots The clique
encoding requires an association graph with $g h$ vertices to be
constructed before search.  Modern maximum-clique algorithms typically perform
a colouring step at each search node that is quadratic in the order of the
graph, and thus $\BigO{n^4}$ in the order of the max common subgraph input
graphs.

>>>>

Let $G$ and $H$ be the two input graphs to our maximum common subgraph problem.
The orders (vertex counts) of these graphs are denoted $g$ and $h$.

@@

\paragraph{Efficient representation of label classes} The algorithm as
described so far apparently requires $\BigO{g(g+h)}$ space at each level of the
search tree.  We can reduce the memory requirement to $\BigO{g+h}$ per level by
storing a \emph{label class} as a pair $\langle P,T \rangle$ for each label $l$
that is used, where $P$ is the set of vertices in $\V(G)$ labelled $l$, and $T$
is the set of vertices in $\V(H)$ labelled $l$\footnote{We adopt terminology
from subgraph isomorphism, where one graph is a pattern graph $P$ and the other
the target graph $T$.}. Since there are $g + h$ vertices in the two graphs, at
most $g + h$ label classes can exist at once, and there are at most $g + h$
vertices in the union of all of the $P$ and $T$ sets.  We can gain further
efficiency by discarding during search any label class that has an empty $P$ or
$T$ set.

@@

\paragraph{Undirected with edge labels} Each adjacency matrix entry contains an
edge label, or a null entry (non-adjacent) $0$.  We use \cref{labDirAlg}, by
letting $L$ be the union of $\{0\}$ with the set of all labels that appear in
the input graphs. Since there may be up to $g + h$ distinct labels, the loop in
\cref{labDirAlg} may execute up to $g + h$ times, resulting in $\BigO{(g+h)^2}$
time complexity per search node.  To achieve $\BigO{(g+h) \log (g+h)}$ time
complexity per search node, we can modify the algorithms to use sorting rather
than explicitly looping over all label classes, as follows.  First, run lines
17-19 of \cref{McCliqueAlg} to create a new label-class of vertices that are
not adjacent to $v$ or $w$, and remove these vertices from $\langle P',T'
\rangle$.  Next, sort $P'$ and $T'$ in ascending order of the label on the edge
from $v$ or $w$ to each vertex. We can then create the label classes
corresponding to each edge label by simultaneously traversing $P'$ and $T'$
from left to right.

@@

\McSplit\ requires $\BigO{g+h}$ time at each search node, and does not require
any auxiliary data structures larger than the adjacency matrices of $G$ and $H$
to be built prior to search.  CP-FC requires $\BigO(?????)$ \dots The clique
encoding requires an association graph with $g h$ vertices to be
constructed before search.  Modern maximum-clique algorithms typically perform
a colouring step at each search node that is quadratic in the order of the
graph, and thus $\BigO{g^2h^2}$ in the order of the max common subgraph input
graphs.
